\LARGE \bf Steering a Swarm Using Global Inputs and Swarm Statistics

### 2016-08-10 journalSwarmControl/realExperiment.tex
A lot os shapes changed
added wrap figure to 3 figures

\subsection{Environmental setup}  
In these experiments as shown in Fig.~\ref{fig:setup}, we used $n$=100 kilobots, a 1.5 m$\times$1.2 m whiteboard as the workspace, and lights: four 50W LED floodlights  at the corners and four 30W LED floodlights on the sides of a 6 m square centered on the workspace and 1.5 m above the table. The lights were controlled using an Arduino Uno board connected to an 8 relay shield board.

@@

The Laser-cut patterns for the neon green fiducial markers on the robots and {\sc Matlab} tracking code are available at our github repository~\cite{Shahrokhi2015GitHubShapeControl}. 
The objects were 3D printed from ABS plastic with a paper overlay. 
Shapes included a 325 cm$^2$ equilateral triangle, 
%Small Equilateral Triangle 140 cm$^2$,
 324 cm$^2$ square,
 281 cm$^2$ hexagon,
254 cm$^2$ circle, 
and a 486 cm$^2$ (18 cm$\times$27 cm)  rectangle.

\begin{figure*}
\begin{center}
	%\includegraphics[width=0.5\columnwidth]{SetUp.pdf}
	\begin{overpic}[width=0.6\columnwidth]{SetUp.pdf}%\put(1,75){A}
	\end{overpic}\\
	\begin{overpic}[width=0.35\columnwidth]{AllShapesR.pdf}%\put(-0,85){B}
	\end{overpic}
	\begin{overpic}[width=0.35\columnwidth]{PotentialExp.pdf}%\put(-0,85){C}
	\end{overpic}
\end{center}

\caption{\label{fig:setup}
(Top) Hardware platform. (Lower left) Four shapes used for hardware experiments. (Lower right) Visualization of potential field. }
\end{figure*}

@@

\begin{figure*}
\begin{center}
	\begin{overpic}[width=\columnwidth]{RealMean}\end{overpic}
%	\begin{overpic}[width=0.35\columnwidth]{XYMeanControl.eps}\end{overpic}
\end{center}
\vspace{-1em}
\caption{\label{fig:realMean}
Regulating average $x$ position of 100 kilobots using control law \eqref{eq:PDcontrolPosition}.
%Mean control plot with kilobots. %\todo{place a red star and a red circle at two spots on graph, put two images of the swar at right with a red star and red circle in left hand corner of these, and put a scale bar in image}
}
\end{figure*}

>>>>

\subsection{Environmental setup}  
In these experiments as shown in Fig.~\ref{fig:setup}, we used $n$=100 kilobots, a 1.5 m$\times$1.2 m whiteboard as the workspace, and lights: four 50W LED floodlights  at the corners and four 30W LED floodlights on the sides of a 6 m square centered on the workspace and 1.5 m above the table. An Arduino Uno connected to an 8 relay shield controlled the lights.

@@

The Laser-cut patterns for the neon green fiducial markers on the robots and {\sc Matlab} tracking code are available at our github repository,~\cite{Shahrokhi2015GitHubShapeControl}. 
The objects were 3D printed from ABS plastic with a paper overlay. 
Shapes included a 325 cm$^2$ equilateral triangle, 
%Small Equilateral Triangle 140 cm$^2$,
 324 cm$^2$ square,
 281 cm$^2$ hexagon,
254 cm$^2$ circle, 
and a 486 cm$^2$ (18 cm$\times$27 cm)  rectangle, all shown in Fig.~\ref{fig:setup}.

%\begin{figure*}
%\begin{center}
%	%\includegraphics[width=0.5\columnwidth]{SetUp.pdf}
%	\begin{overpic}[width=0.6\columnwidth]{SetUp.pdf}%\put(1,75){A}
%	\end{overpic}\\
%	\begin{overpic}[width=0.35\columnwidth]{AllShapesR.pdf}%\put(-0,85){B}
%	\end{overpic}
%	\begin{overpic}[width=0.35\columnwidth]{PotentialExp.pdf}%\put(-0,85){C}
%	\end{overpic}
%\end{center}
%\caption{\label{fig:setup}
%(Top) Hardware platform. (Lower left) Four shapes used for hardware experiments. (Lower right) Visualization of potential field. }
%\end{figure*}

\begin{figure*}
\begin{center}
	%\includegraphics[width=0.5\columnwidth]{SetUp.pdf}
	\begin{overpic}[width=0.5\columnwidth]{SetUp.pdf}%\put(1,75){A}
	\end{overpic}\begin{overpic}[width=0.25\columnwidth]{AllShapesR.pdf}%\put(-0,85){B}
	\end{overpic}\begin{overpic}[width=0.25\columnwidth]{PotentialExp.pdf}%\put(-0,85){C}
	\end{overpic}
\end{center}
\caption{\label{fig:setup}
Hardware platform. At right are the shapes used for hardware experiments and a visualization of the potential field. }
\end{figure*}

@@

\begin{figure*}
\begin{center}
	\begin{overpic}[width=\columnwidth]{RealMean}\put(42,20){\emph{t}= 90 s}\put(72,20){\emph{t}= 175 s}\end{overpic}
%	\begin{overpic}[width=0.35\columnwidth]{XYMeanControl.eps}\end{overpic}
\end{center}
\vspace{-1em}
\caption{\label{fig:realMean}
Regulating average $x$ position of 100 kilobots using control law \eqref{eq:PDcontrolPosition}.
%Mean control plot with kilobots. %\todo{place a red star and a red circle at two spots on graph, put two images of the swar at right with a red star and red circle in left hand corner of these, and put a scale bar in image}
}
\end{figure*}

### 2016-08-10 journalSwarmControl/theory.tex
added wrap figure to 3 figures

\If{$\sigma_y^2 > \sigma_{max}^2$}
\State $y_{goal}  \gets y_{min}$
\State $flag_y  \gets \TRUE$
\Else {\bf~if} {$flag_y$ \textbf{and} $\sigma_y^2 < \sigma_{min}^2$}
\State $y_{goal}  \gets  y_{target}$
\State $flag_y  \gets \FALSE$
\EndIf
\State Apply \eqref{eq:PDcontrolPosition} to move toward $[x_{goal}, y_{goal}]$
\EndLoop
\end{algorithmic}
\end{algorithm}
\begin{figure}
\centering
\begin{overpic}[scale=.3]{hysteresis.png}
\put(39,21){$\sigma^2(\mathbf{x}) < \sigma^2_{min}$ }
\put(39,5){$\sigma^2(\mathbf{x}) > \sigma^2_{max}$}\end{overpic}
\vspace{-1em}
\caption{\label{fig:hysteresis} Two states to control mean and variance of a robot swarm.
%\vspace{-2em}
}
\end{figure}

A key challenge is to select proper values for $\sigma_{min}^2$ and $\sigma_{max}^2$.  The optimal packing variance was given in \eqref{eq:optimalvar}.
The random packings generated by pushing our robots into corners are suboptimal, so we choose the conservative values shown in Fig.~\ref{fig:VarianceMinMaxBand}:
\begin{align}
 \sigma^2_{min} &= 2.5r+ \sigma^2_{optimal}(n,r) \nonumber\\
  \sigma^2_{max} &= 15r+ \sigma^2_{optimal}(n,r).
  \end{align}
%\sigma \approx 0.371258 n r,   \sigma_{min} = n*r*1/2, \sigma_{min} = n*r*3/2, 
%  this result was verified in http://www-math.mit.edu/~tchow/penny.pdf

@@

\begin{figure}
\centering
\begin{overpic}[width = 0.5\columnwidth]{VarianceMinMaxBand2v2.pdf}\end{overpic}
\vspace{-1em}
\caption{\label{fig:VarianceMinMaxBand} The switching conditions for variance control are set as a function of $n$, and designed to be larger than the optimal packing density. The above plot uses robot radius $r=1/10$.
}\vspace{-1em}
\end{figure}

>>>>

\If{$\sigma_y^2 > \sigma_{max}^2$}
\State $y_{goal}  \gets y_{min}$
\State $flag_y  \gets \TRUE$
\Else {\bf~if} {$flag_y$ \textbf{and} $\sigma_y^2 < \sigma_{min}^2$}
\State $y_{goal}  \gets  y_{target}$
\State $flag_y  \gets \FALSE$
\EndIf
\State Apply \eqref{eq:PDcontrolPosition} to move toward $[x_{goal}, y_{goal}]$
\EndLoop
\end{algorithmic}
\end{algorithm}

\begin{figure}
\centering
\begin{overpic}[width = 0.5\columnwidth]{hysteresis.png}
\put(33,21){$\sigma^2(\mathbf{x}) < \sigma^2_{min}$ }
\put(33,5){$\sigma^2(\mathbf{x}) > \sigma^2_{max}$}\end{overpic}
\begin{overpic}[width = 0.45\columnwidth]{VarianceMinMaxBand2v2.pdf}\end{overpic}
\vspace{-0.5em}
\caption{\label{fig:hysteresis} (Left) Two states to control mean and variance of a robot swarm. 
(Right) Switching conditions for variance control are set as a function of $n$, and designed to be larger than the optimal packing density. The plot uses robot radius $r=1/10$.
%\vspace{-2em}
}
\end{figure}

%\begin{figure}
%\centering
%\begin{overpic}[width = 0.5\columnwidth]{VarianceMinMaxBand2v2.pdf}\end{overpic}
%\vspace{-1em}
%\caption{\label{fig:VarianceMinMaxBand} The switching conditions for variance control are set as a function of $n$, and designed to be larger than the optimal packing density. The above plot uses robot radius $r=1/10$.
%}\vspace{-1em}
%\end{figure}

A key challenge is to select proper values for $\sigma_{min}^2$ and $\sigma_{max}^2$.  The optimal packing variance was given in \eqref{eq:optimalvar}.
The random packings generated by pushing our robots into corners are suboptimal, so we choose the conservative values shown in Fig.~\ref{fig:hysteresis}:
\begin{align}
 \sigma^2_{min} &= 2.5r+ \sigma^2_{optimal}(n,r) \nonumber\\
  \sigma^2_{max} &= 15r+ \sigma^2_{optimal}(n,r).
  \end{align}
%\sigma \approx 0.371258 n r,   \sigma_{min} = n*r*1/2, \sigma_{min} = n*r*3/2, 
%  this result was verified in http://www-math.mit.edu/~tchow/penny.pdf

@@
